A comparison of classification algorithms applied to the Adult Database

### 2009-12-17 demo/demo.tex
fixing typos in the presentation.

    \begin{itemize}
    \item 48842 entries of individual information of people gathered in a 1994 census on the United States of America.
    \begin{itemize}
        \item 32561 records for the training set (67\%).
        \item 16281 records for the test set (33\%).
    \end{itemize}
    \item Each entry is composed by a set of 14 attributes and 2 classes (winning more or less than 50K dollars a year).
    \item There are 3620 records with missing values. The only attributes containing missing values are \textbf{Workclass}, \textbf{Occupation} and \textbf{Native-country}.
    \item Available in \url{ftp://ftp.ics.uci.edu/pub/machine-learning-databases/adult}.
    \end{itemize}
}

@@

  \begin{itemize}
    \item Classifiers were built using the train set and then tested against the test set
    \item C4.5, Random Forest, CART, ADTree and Bayesian classifiers built using Weka
    \begin{itemize}
      \item Various parameters available in Weka algorithms were experimented in hope of getting better error rates
      \item Every missing value was replaced with modes and means
      \item Two different classifiers were trained for each algorithm, one using only discretized attributes
                and another with the attributes unmodified
      \item Analyze how the algorithm behaves when using numeric attributes
    \end{itemize}
  \end{itemize}
}

@@

  \begin{itemize}
    \item RapidMiner was used to build a classifier with the ID3 algorithm.
    \item Peter Clark's CN2 was used to induce rules.
    \begin{itemize}
        \item \url{http://www.cs.utexas.edu/users/pclark/software/\#cn2}.
    \end{itemize}
    \item Aleph was used to inductively generate logic clauses.
    \begin{itemize}
        \item \url{http://www.comlab.ox.ac.uk/activities/machinelearning/Aleph/aleph.html}.
    \end{itemize}
  \end{itemize}
}

@@

  \begin{itemize}
    \item Weka supports a confidence threshold parameter that dictates how much pruning the algorithm will do
    \item The bigger the threshold the less pruning the algorithm does
    \item When using only discretized data the algorithm gives error rates of $\approx$25\%
  \end{itemize}

@@

  \begin{itemize}
    \item It is an ensemble classifier consisting of many decision trees
    \item Outputs the class that is the mode of the class's output by individual trees
    \item Better results require more time building the classifier
    \item Large quantities of memory needed: 1GB to compute with 400 trees
    \item Over-fitting
  \end{itemize}

@@

  \begin{itemize}
    \item Based on conditional probabilities and the Bayes theorem
    \item Represents a set of variables and their conditional independencies via a directed acyclic graph and a set of probability tables
    \item The algorithm first learns the network structure / graph and then learns the probability tables
    \item We experimented with different algorithms to learn the network structure:
     \begin{itemize}
      \item Genetic Search
      \item Hill Climbing
      \item Simulated Annealing
     \end{itemize}
    \item Weka provides a very rich set of parameters for each search algorithm
  \end{itemize}

>>>>

    \begin{itemize}
    \item 48842 entries of individual information of people gathered in a 1994 census on the United States of America.
    \begin{itemize}
        \item 32561 records for the training set (67\%).
        \item 16281 records for the test set (33\%).
    \end{itemize}
    \item Each entry is composed by a set of 14 attributes and a class (winning more or less than 50K dollars a year).
    \item There are 3620 records with missing values. The only attributes containing missing values are \textbf{Workclass}, \textbf{Occupation} and \textbf{Native-country}.
    \item Available in \url{ftp://ftp.ics.uci.edu/pub/machine-learning-databases/adult}
    \end{itemize}
}

@@

  \begin{itemize}
    \item Classifiers were built using the train set and then tested against the test set.
    \item C4.5, Random Forest, CART, ADTree and Bayesian classifiers built using Weka:
    \begin{itemize}
      \item Various parameters available in Weka algorithms were experimented in hope of getting better error rates.
      \item Every missing value was replaced with modes and means.
      \item Two different classifiers were trained for each algorithm, one using only discretized attributes
                and another with the attributes unmodified.
      \item Analyze how the algorithm behaves when using numeric attributes.
    \end{itemize}
  \end{itemize}
}

@@

  \begin{itemize}
    \item RapidMiner was used to build a classifier with the ID3 algorithm.
    \item Peter Clark's CN2 was used to induce rules.
    \begin{itemize}
        \item \url{http://www.cs.utexas.edu/users/pclark/software/\#cn2}
    \end{itemize}
    \item Aleph was used to inductively generate logic clauses.
    \begin{itemize}
        \item \url{http://www.comlab.ox.ac.uk/activities/machinelearning/Aleph/aleph.html}
    \end{itemize}
  \end{itemize}
}

@@

  \begin{itemize}
    \item Weka supports a confidence threshold parameter that dictates how much pruning the algorithm will do.
    \item The bigger the threshold the less pruning the algorithm does.
    \item When using only discretized data the algorithm gives error rates of $\approx$25\%.
  \end{itemize}

@@

  \begin{itemize}
    \item It is an ensemble classifier consisting of many decision trees.
    \item Outputs the class that is the mode of the class's output by individual trees.
    \item Better results require more time building the classifier.
    \item Large quantities of memory needed: 1GB to compute with 400 trees.
    \item Over-fitting.
  \end{itemize}

@@

  \begin{itemize}
    \item Based on conditional probabilities and the Bayes theorem.
    \item Represents a set of variables and their conditional independencies via a directed acyclic graph and a set of probability tables.
    \item The algorithm first learns the network structure / graph and then learns the probability tables.
    \item We experimented with different algorithms to learn the network structure:
     \begin{itemize}
      \item Genetic Search
      \item Hill Climbing
      \item Simulated Annealing
     \end{itemize}
    \item Weka provides a very rich set of parameters for each search algorithm.
  \end{itemize}
